---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# kielr

<!-- badges: start -->
<!-- badges: end -->

The goal of the package kielr is to provide quizzes accompanying the courses of the [Data Science Master Program](https://www.fh-kiel.de/fachbereiche/data-science-interdisziplinaerer-studiengang/) at [University of Applied Science Kiel](https://www.fh-kiel.de/).

## Installation

You can install the development version of kielr from [Github](https://github.com/tillschwoerer/kielr) with:

```{r}
devtools::install_github("tillschwoerer/kielr", ref = "main")
```

You also need to install the package **learnr** with:

```{r}
install.packages('learnr')
```


## Example

To check which tutorials are available run
```{r eval=FALSE}
learnr::available_tutorials("kielr")
```
To run a specific tutorial run, e.g.
```{r example, eval=FALSE}
learnr::run_tutorial("programming1", "kielr")